---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# mmpipe

Install with `devtools::install_gh("moodymudskipper/mmpipe")`

This package proposes new pipe operators, a function to define custom operators
easily, 2 other pipe friendly functions for conditional steps or printing.

* **%W>%** : silence **w**arnings
* **%V>%** : uses `View()` on the output
* **%L>%** : **L**ogs the relevant call to the console
* **%P>%** : uses `print()` on the output
* **%S>%** : prints the `summary()` of the output
* **%G>%** : uses `tibble::glimpse` on the output
* **%D>%** : **D**ebugs the pipe chain at the relevant step
* **%C>%** : **C**locks the relevant step
* **add_pipe** : build custom pipe
* **pif** : conditional steps
* **pprint** : pipe friendly printing
* **-.gg** : Just like `%>%` but the different operator precedence makes it
sometimes more convenient.

`magrittr`'s operators are also exported so they can be used without attaching
alias functions.

## new operators

When we attach `mmpipe` the functions `magrittr:::is_pipe` and 
`magrittr:::wrap_function` are modified to register our new pipes in the
package, thus a couple warnings are displayed.

```{r}
library(mmpipe)
```

silence a warning:

```{r}
data.frame(a = c(1,-1)) %W>% transform(a = sqrt(a))
```

log steps in the console:

```{r}
iris %L>% {Sys.sleep(1);head(.,2)} %L>% {Sys.sleep(2);.[4:5]}
```

use print, summary or glimpse on output:

```{r}
iris %P>% head(2) %P>% `[`(4:5)

iris %S>% head(2) %S>% `[`(4:5)

iris %G>% head(2) %G>% `[`(4:5)
```

view steps of chain in the viewer:

```{r, eval = FALSE}
iris %V>% head(2) %V>% `[`(4:5)

```

debug the chain:

```{r}
iris %>% head(2) %D>% `[`(4:5)
```

time operations:

```{r}
iris %C>% head(2) %C>% {Sys.sleep(2);.} 
```


## Create your own pipe operators with `add_pipe`

We create an operator by feeding to `add_pipe` its raw name and the modified
body of the expression a regular pipe call would return. 

the operator is created and *magrittr*'s namespace is modified to make the new 
operator compatible.

This is not obvious so let's see some examples, if we wanted to recreate 
existing operators.

Redefining `%P2>%` as `%P>%` twin :

```{r}
 add_pipe(`%P2>%`, substitute({. <- print(b);cat("\n"); .}, list(b = body)))
 iris %P2>% head(3) %>% head(2)
```

Redefining `%T2>%` as `%T>%` twin :

```{r}
 add_pipe(`%T2>%`, call("{", body, quote(.)))
 iris %T2>% {message("side effect")} %>% head(2)
```

Redefining `%W2>%` as `%W>%` twin :

```{r}
 add_pipe(`%W2>%`, substitute(
     {options(warn = -1); on.exit(options(warn = w)); b},
     list(w = options()$warn, b = body)))
 data.frame(a = c(1,-1)) %W2>% transform(a = sqrt(a))
```

See `magrittr:::wrap_function`'s code for a better understanding.

See also functions `rm_pipe` and `list_pipes`.

## easy conditional steps with `pif`

Using functions:

```{r}
iris %>% pif(is.data.frame, dim, nrow)
```

Using formulas:

```{r}
iris %>% pif(~is.numeric(Species), ~"numeric :)",~paste(class(Species)[1],":("))

```

Using raw expressions:

```{r}
iris %>% pif(nrow(iris) > 2, head(iris,2))

```

Be careful with expressions!

```{r}
iris %>% pif(TRUE, dim,  warning("this will be evaluated"))
iris %>% pif(TRUE, dim, ~warning("this won't be evaluated"))
```

## print info on intermediate steps with `pprint`

```{r}
library(ggplot2)
iris %>%
  pprint(~"hello")           %>%
  head(2)                    %>%
  transform(Species = NULL)  %>%
  pprint(rowSums,na.rm = TRUE) %>%
  pprint(~setNames(.[1:2],toupper(names(.[1:2])))) %>%
  pprint(dim)
```
