---
title: "mmpipe"
author: "Antoine Fabri"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## mmpipe

Install with `devtools::install_gh("moodymudskipper/mmpipe")`

This package propose 5 new pipe operators, a function to define custom operators
easily, and a few helper functions.

`magrittr`'s operators are also exported so they can be used without attaching*
its aliases functions.

## new operators

The figure sizes have been customised so that you can easily put two images side-by-side.

```{r}
library(mmpipe)

# silence a warning
data.frame(a = c(1,-1)) %W>% transform(a=sqrt(a))

# log steps in the console
iris %L>% {Sys.sleep(1);head(.,2)} %L>% {Sys.sleep(2);.[4:5]}

# use print, summary or glimpse on output
iris %P>% head(2) %P>% `[`(4:5)

iris %S>% head(2) %S>% `[`(4:5)

iris %G>% head(2) %G>% `[`(4:5)
```

```{r, eval = FALSE}
# view steps of chain in the viewer
iris %V>% head(2) %V>% `[`(4:5)

# debug the chain
iris %>% head(2) %D>% `[`(4:5)
```

## Create your own pipe operators with `add_pipe`

If we wanted to recreate existing operators

```{r}
 add_pipe(`%T2>%`, call("{", body, quote(.)))
 iris %T2>% {message("side effect")} %>% head(2)
 add_pipe(`%W2>%`, substitute(
     {options(warn = -1); on.exit(options(warn = w)); b},
     list(w = options()$warn, b = body)))
 data.frame(a = c(1,-1)) %W2>% transform(a = sqrt(a))
 add_pipe(`%P2>%`, substitute({. <- print(b);cat("\n");.}, list(b = body)))
 iris %P>% head(3) %>% head(2)
```

## easy conditional steps with `pif

```{r}
# using functions
iris %>% pif(is.data.frame, dim, nrow)
# using formulas
iris %>% pif(~is.numeric(Species), ~"numeric :)",~paste(class(Species)[1],":("))
# using expressions
iris %>% pif(nrow(iris) > 2, head(iris,2))
# careful with expressions
iris %>% pif(TRUE, dim,  warning("this will be evaluated"))
iris %>% pif(TRUE, dim, ~warning("this won't be evaluated"))
```

## print info on intermediate steps with `pprint`

```{r}
iris %>%
pprint(~"hello")           %>%
head(2)                    %>%
transform(Species = NULL)  %>%
pprint(rowSums,na.rm = TRUE) %>%
pprint(~setNames(.[1:2],toupper(names(.[1:2])))) %>%
pprint(dim)
```
